Cognitive Analysis

### 2024-07-25 Manuscript Analysis/manuscript_analysis.Rmd
Listener demo and cog summary

@@

#

@@

plot(pressure)

@@

>>>>

# Load in the listener demographics data

demo <- rio::import("Cleaned Data/cleaned_listener_demo.csv") |>
  dplyr::filter(pupil_complete == "complete") |>
  dplyr::select(id, age, gender, ethnicity, race, native_lang) |>
  dplyr::mutate(gender = factor(gender, levels = c("Man", "Woman", "Nonbinary", "Questioning", "Prefer not to answer")),
                ethnicity = factor(ethnicity, levels = c("Hispanic/Latino(a/e)", "Not Hispanic/Latino(a/e)", "Prefer not to answer")),
                race = factor(race, levels = c("white/Caucasian", "Black/African American", "Asian/Asian American",
                                               "Native Hawaiian or Other Pacific Islander", "Native American or Alaska Native",
                                               "Biracial or Multiracial", "Race not listed", "Prefer not to answer")),
                native_lang = factor(native_lang, c("American English", "Not American English"))) |>
  dplyr::rename(subject = id)

# Loading in the cog data

cog <- rio::import("Cleaned Data/cleaned_cog_data.csv")

# Loading in the pupil data

pupil <- rio::import("Cleaned Data/cleaned_pupil_data_normalized.csv")

# Loading in the phrase accuracy data

phrase_acc <- rio::import("Cleaned Data/repetition_accuracy.csv") |>
  dplyr::mutate(rep_acc = ifelse(initial_response == "missing data", NA, 
                                 ifelse(target_number == correct_words_initial, "accurate", "inaccurate")),
                rep_acc_rel = ifelse(rel_response == "missing data", NA, 
                                 ifelse(target_number == correct_words_rel, "accurate", "inaccurate")))

@@

# Listener Demographics

The listeners used in this study are the same from the parent study. In brief, the demographic information from these listeners are below.

@@

demo_table <- demo |>
  dplyr::select(age, gender, ethnicity, race, native_lang) |>
  tbl_summary(type = list(age ~ "continuous",
                          gender ~ "categorical",
                          ethnicity ~ "categorical",
                          race ~ "categorical",
                          native_lang ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} ({p}%)"),
              digits = list(everything() ~ c(2)),
              label = list(age ~ "Age",
                           gender ~ "Gender",
                           ethnicity ~ "Ethnicity",
                           race ~ "Race",
                           native_lang ~ "Native Language")) |>
  as_gt()

demo_table

demo_table |>
  gt::gtsave("Tables/demo_table.html")

@@

# Listener Cognition

cog_table <- cog |>
  dplyr::select(-subject) |>
  # Just using the age-corrected scores
  dplyr::select(ends_with("_c")) |>
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(everything() ~ c(2)),
              label = list(list_sort_c ~ "Working Memory",
                           flanker_c ~ "Inhibitory Control",
                           card_sort_c ~ "Cognitive Flexibility",
                           pattern_c ~ "Processing Speed")) |>
  as_gt()

cog_table

cog_table |>
  gt::gtsave("Tables/cog_table.html")
